---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

# fmr

<!-- badges: start -->
<!-- badges: end -->

The goal of {fmr} is to:

* Establish R-connection to [Fisheries Technologies](https://fishtech.is) [The Fisheries Manager](https://fimsehf.atlassian.net/wiki/spaces/FT/overview?homepageId=3175186440) data
  * The current communication is via API's that provides data in json-format
* Provide convenient functions to FTM tables and views
* Provide markdown report templates for various standardized reports
* R-code examples for data analysis and graphical presentations

## Quick start

```{r, eval = FALSE}
remotes::install_github("einarhjorleifsson/fmr")
```


```{r}
library(fmr)
library(tidyverse)
key <- "your FM API key"
```

```{r, echo = FALSE, include = FALSE}
key <- Sys.getenv("fm_key")
```

```{r}
fm_survey(key) |> glimpse()
```


