---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

# fmr

<!-- badges: start -->
<!-- badges: end -->

The goal of {fmr} is to:

* Establish R-connection to [The Fisheries Manager](https://fimsehf.atlassian.net/wiki/spaces/FT/overview?homepageId=3175186440) data provided by [Fisheries Technologies](https://fishtech.is) 
  * The current communication is via API's that provides data in json-format
* Provide wrapper functions to FTM tables and views
* Provide markdown report templates for various standardized reports
* R-code examples for data analysis and graphical presentations

## Installing

```{r, eval = FALSE}
remotes::install_github("einarhjorleifsson/fmr")
```

## Connection

```{r}
library(fmr)
library(tidyverse)
key <- "your_FM_API_key"
```

```{r, echo = FALSE}
key <- Sys.getenv("fm_key")
```

## The FM API

The current API does not provide direct access to the database used by FM (Oracle) but to an API that provides the data in a JSON format. An example of such an interface (here for the gear table) is:


### Primary tables

Currently there are three primary datatables within the FM-system:

* ...

### Auxillary tables

* ...


## The {fmr} philosophy

The {fmr}-package provides a convenient wrapper to the FM-API so that data can be imported directly into R. The lowest level function is `fm_tbl`-function. One can e.g. obtain an exact copy of the what can be obtained from the JSON API "surveyItem" (read: The trip table) by using the following arguments:

```{r}
fm_tbl(table = "surveyItem", key = key, clean = FALSE) |> glimpse()
```

This table has actually a lot of variables, starting off with a lot of numerical "Id"s that an average data analyst may be unfamiliar with. ...

There are also two addtional notes to make with respect to these "raw" data:

* Variable names are in "camel-toe" format meaning some letters are capital format
* Some of the variable types are not as expected. Examples are all the datetime variables (depTime, arrTime, createdDate, lastModifiedDate) are set as characters. And then we have a lot of variables that are of type logigcal (<lgl>)

The reason for the latter is that the API JSON format does not provide type specification of each variable and R imports variables based on the "lowest denominator".




Most of the function only need the user to supply the FM-API **key*, it being strategically put as the first argument. So e.g. to access the trip table one only needs the following:

```{r}
fm_trip(key, std = FALSE) |> glimpse()
```



```{r}
fm_tbl(table = "vesselD", key) |> glimpse()
```



