---
title: "QC report"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r}
# PUT THE YEAR AND THE MONTH YOU WANT TO DO QC
YEAR  <- 2024
MONTH <- 2
```

```{r}
library(fmr)
library(tidyverse)
key <- "Your FM API key"
```

```{r, echo = FALSE}
key <- Sys.getenv("fm_key")
```

## Preamble

This document is currently a combination of notes and some ad-hoc code associated with quality control. In the end we expect to have a more succinct document that only deals with the quality control.

## The survey table

We (I) expect that the information in the survey table is refecting information about the whereabout and time that an observer was surveying.

```{r}
survey <- 
  # want all the columns here, hence trim FALSE
  fmr::fm_survey(key, trim = FALSE) |> 
  filter(year(date) == YEAR,
         month(date) == MONTH)
```

### We do expect survey's to start and end within the same date

```{r}
survey |> 
  filter(date(T1) != date(T2)) |> 
  select(site, date, survey_id, status, collector, T1, T2) |> 
  arrange(site, date, collector) |> 
  knitr::kable()
```

### We do not expect survey's being done on a Saturday or Sunday

```{r}
survey |> 
  mutate(wday = wday(date, label = TRUE, locale = "en_GB.utf8", week_start = 1)) |> 
  filter(wday %in% c("Sat", "Sun")) |> 
  select(site, date, wday, survey_id, status, collector) |> 
  arrange(site, date, collector) |> 
  knitr::kable()
```

### We do not expect more than one survey entry per observer per sampling day

```{r}
d <- 
  survey |> 
  group_by(site, date, collector) |> 
  summarise(n = n(),
            .groups = "drop")
# List of sites, date and collector with more than one survey id
d |> 
  filter(n > 1) |> 
  knitr::kable(caption = "Number of distinct survey_id's by site, date and collector")
# Get a list of the survey id's behind these records
d |> 
  filter(n > 1) |> 
  left_join(survey) |> 
  select(site:n, survey_id, status, T1, T2) |> 
  knitr::kable(caption = "List of survey_id's")
```

NOTE: Ideally we would like to have one survey_id per landing site irrespective of the number of surveyor's. I guess in order to do achieve that one need to setup the anticipated survey date beforehand and then each of the observers log into that same survey_id.

